Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-20 analysis/supplementary materials/Supplementary Materials.Rmd
Add plots to supplementary materials

```{r, setup, echo = FALSE, message=FALSE}

library("Reproducibility.in.Plant.Pathology")
library("tidyverse")
library("pander")
library("report")
library("flextable")

@@

@@

@@

@@

@@

@@

>>>>

```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}

library("Reproducibility.in.Plant.Pathology")
library("tidyverse")
library("pander")
library("report")
library("flextable")
library("bayestestR")

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_f1))
```

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_f2))
```

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_g1))
```

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_g2))
```

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_h1))
```

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
plot(equivalence_test(m_h2))
```
